Black-hole ringdown as a probe of higher-curvature gravity theories

### 2022-01-20 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
HS: added eft bh refs.

\documentclass[twocolumn,prd,aps,superscriptaddress,preprintnumbers,tightenlines,showpacs,nofootinbib,eqsecnum,amsfonts,amsmath,longbibliography]{revtex4-1}
\usepackage{epsfig}
\usepackage{graphics}
\usepackage{graphicx}
\usepackage[dvipsnames]{xcolor}
\usepackage{bm}
% \usepackage{txfonts}
\usepackage{amssymb}
\usepackage{xspace}
\usepackage[normalem]{ulem} % To get strikethrough (\sout)
\usepackage[colorlinks]{hyperref}
\usepackage[caption=false]{subfig}
\usepackage{booktabs}
\usepackage{url}
\usepackage{float}
\usepackage[bottom]{footmisc}
\usepackage{lineno}
\usepackage{mathrsfs}
\usepackage{makecell}
\usepackage{microtype}

@@

\newcommand{\lame}{\lambda_{\rm e}}
\newcommand{\lamo}{\lambda_{\rm o}}
\newcommand{\acs}{\ell_{\rm CS}}
\newcommand{\agb}{\ell_{\rm GB}}

@@

We will consider several modified gravity theories as applications of the \pSEOB{}
waveform model presented in Sec.~\ref{sec:review_pSEOB}.
%
In the following, we briefly review which theories we consider, what are the
currents observational constraints in each of them and what we known about the
QNMs of black holes in each of them.

\subsection{scalar-Gauss-Bonnet gravity}
%
This theory is given by the following action,
%
\begin{equation} \label{eq:action_sgb}
    S_{\rm GB} = \frac{1}{16 \pi}
    \int \dV
    \left[
    R - \tfrac{1}{2}(\nabla \varphi)^2
    + \tfrac{1}{4} \ell^{2}_{\rm GB} f(\varphi) \mathscr{G}
    \right],
\end{equation}
%
where $R$ is the Ricci scalar associated with the metric $g_{\alpha\beta}$ and
$\varphi$ is a dynamical scalar field which couples to the Gauss-Bonnet
invariant $\mathscr{G}$,
%
\begin{equation} \label{eq:def_gb}
    \mathscr{G} =
    R^{\mu\nu\rho\sigma}R_{\mu\nu\rho\sigma}
    - 4 R^{\mu\nu}R_{\mu\nu}
    + R^2,
\end{equation}
%
with strength set by the dimensionful coupling constant $\agb$ with dimensions
of length.

@@

Black holes in these theories were studied in \dots

@@

% \bibliographystyle{apsrev}
\bibliography{paper_alt_theor_bounds}

>>>>

\documentclass[twocolumn,prd,aps,superscriptaddress,preprintnumbers,tightenlines,showpacs,nofootinbib,eqsecnum,amsfonts,amsmath,longbibliography]{revtex4-1}
\usepackage{epsfig}
\usepackage{graphics}
\usepackage{graphicx}
\usepackage[dvipsnames]{xcolor}
\usepackage{bm}
% \usepackage{txfonts}
\usepackage{natbib}
\usepackage{amssymb}
\usepackage{xspace}
\usepackage[normalem]{ulem} % To get strikethrough (\sout)
\usepackage[colorlinks]{hyperref}
\usepackage[caption=false]{subfig}
\usepackage{booktabs}
\usepackage{url}
\usepackage{float}
\usepackage[bottom]{footmisc}
\usepackage{lineno}
\usepackage{mathrsfs}
\usepackage{makecell}
\usepackage{microtype}

@@

\newcommand{\lame}{\lambda_{\rm e}}
\newcommand{\lamo}{\lambda_{\rm o}}

@@

% We will consider several modified gravity theories as applications of the \pSEOB{}
% waveform model presented in Sec.~\ref{sec:review_pSEOB}.
%
We briefly review which theories we consider, what are the currents
observational constraints in each of them and what we known about the QNMs of
black holes in each of them.

\subsection{scalar-Gauss-Bonnet gravity}
%
This theory is given by the following action,
%
\begin{equation} \label{eq:action_sgb}
    S_{\rm GB} = \frac{1}{16 \pi}
    \int \dV
    \left[
    R - \tfrac{1}{2}(\nabla \varphi)^2
    + \tfrac{1}{4} \ell^{2}_{\rm GB} f(\varphi) \mathscr{G}
    \right],
\end{equation}
%
where $R$ is the Ricci scalar associated with the metric $g_{\alpha\beta}$ and
$\varphi$ is a dynamical scalar field which couples to the Gauss-Bonnet
invariant $\mathscr{G}$,
%
\begin{equation} \label{eq:def_gb}
    \mathscr{G} =
    R^{\mu\nu\rho\sigma}R_{\mu\nu\rho\sigma}
    - 4 R^{\mu\nu}R_{\mu\nu}
    + R^2,
\end{equation}
%
with strength set by the dimensionful coupling constant $\ell_{\rm GB}$ with dimensions
of length.

@@

Black holes in these theories were found in Refs.~\cite{deRham:2020ejn,Cano:2020cao} for the dimension-six EFT
and in Refs.~\cite{Cardoso:2018ptl} for the dimension-eight EFT.

@@

% \bibliographystyle{apsrev}
\bibliography{biblio}
